--- 
title: "ND111 - Data Science II - Notebook"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---

# Course Info {-}

<h4>Tags</h4>

* Author       : AH Uyekita
* Dedication   : 10 hours/week (suggested)
* Start        : 14/12/2018
* End (Planned): 28/12/2018
* Title        : Data Science II - Foundations Nanodegree Program
    * COD      : ND111

<h4>Related Courses</h4>

* [ND110 - Data Science I - Nanodegree Foundations][nd110]

[nd110]: https://br.udacity.com/course/python-fundamentos-data-science--nd110

***************************************************************************************************

<h2>Objectives</h2>

I want to finish this course in two weeks. It includes the Optional videos and chapters.

<h2>Syllabus</h2>

* Chapter 01 - Welcome
    * Lesson 01 - Instructions
    * Lesson 02 - Tips
* Chapter 02 - SQL for Data Analysis
    * Lesson 01 - Basic SQL
    * Lesson 02 - SQL Joins
    * Lesson 03 - SQL Aggregations
    * Lesson 04 - (Optional) SQL Subqueries & Temporary Tables (Advanced)
    * Lesson 05 - (Optional) SQL Data Cleaning (Advanced)
    * Project 01 - Query a Digital Music Store Database
* Chapter 03 - Data Wrangling
    * Lesson 01 - Introduction to Data Wrangling
    * Lesson 02 - Gathering
    * Lesson 03 - Assessing Data
    * Lesson 04 - Cleaning Data
    * Project 02 - Wrangle and Analyze Data
* Chapter 04 - Advanced Statistics
    * Lesson 01 - Descriptive Statistics - Part 1
    * Lesson 02 - Descriptive Statistics - Part 2
    * Lesson 03 - Admissions Case Study
    * Lesson 04 - Probability
    * Lesson 05 - Binomial Distribution
    * Lesson 06 - Conditional Probability
    * Lesson 07 - Bayes Rule
    * Lesson 08 - Python Probability Practice
    * Lesson 09 - Normal Distribution Theory
    * Lesson 10 - Sampling Distributions and the Central Limit Theorem
    * Lesson 11 - Confidence Intervals
    * Lesson 12 - Hypothesis Testing
    * Lesson 13 - Case Study: A/B Tests
    * Lesson 14 - Regression
    * Lesson 15 - Multiple Linear Regression
    * Lesson 16 - Logistic Regression
    * Project 03 - Analyze A/B Test Results
* Chapter 05 - Intro to Machine Learning
    * Lesson 01 - Welcome to Machine Learning
    * Lesson 02 - Naive Bayes
    * Lesson 03 - SVM
    * Lesson 04 - Decision Trees
    * Lesson 05 - Choose Your Own Algorithm
    * Lesson 06 - Datasets and Questions
    * Lesson 07 - Regressions
    * Lesson 08 - Outliers
    * Lesson 09 - Clustering
    * Lesson 10 - Feature Scaling
    * Lesson 11 - Text Learning
    * Lesson 12 - Feature Selection
    * Lesson 13 - PCA
    * Lesson 14 - Validation
    * Lesson 15 - Evaluation Metrics
    * Lesson 16 - Tying It All Together
    * Project 04 - Identify Fraud from Enron Email
* Chapter 06 - (Optional) Data Visualization
    * Lesson 01 - Introduction to Data Visualization
    * Lesson 02 - Design
    * Lesson 03 - Data Visualization in Tableau
    * Lesson 04 - Making Dashboard & Stories in Tableau

<h3>Repository Structure</h3>

This is the structure of this repository, each course's chapters (or parts) will be stored in different folders.

```
ND111_data_science_foundation_02
|
+--  01-Chapter_01
|           |
|           +--  README.md                       # General information
|
+--  02-Chapter_02
|           |
|           +--  README.md                       # General information
|           +--  00-Project_01                   # Project 01
|           +--  01-Lesson_01                    # Files from Lesson 01
|           |        +--  README.md              # Notes from Lesson 01 from Chapter 02
|           +--  02-Lesson_02                    # Files from Lesson 02
|           |        +--  README.md              # Notes from Lesson 02 from Chapter 02
|           .
|
+--  03-Chapter_03
|           |
|           +--  README.md                       # General information
|           +--  00-Project_02                   # Project 02
|           +--  01-Lesson_01                    # Files from Lesson 01
|           |        +--  README.md              # Notes from Lesson 01 from Chapter 02
|           +--  02-Lesson_02                    # Files from Lesson 02
|           |        +--  README.md              # Notes from Lesson 02 from Chapter 02
|           .
```

<h3>Best practice</h3>

* Add all _deliverables_ in the [`GitKraken Glo`][bp_1];
* Take notes using the [`Markdown`][bp_2].

[bp_1]: https://www.gitkraken.com/invite/5Ua2spL4
[bp_2]: https://github.com/adam-p/markdown-here/wiki/Markdown-Cheatsheet

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(.packages(), 'bookdown', 'knitr', 'rmarkdown'), 'packages.bib')
```

```{r,message=FALSE,include=FALSE}
# Saving the original Work Directory
original_wd <- getwd()

# Goes to the parents level - Where the files will be rendered
setwd('..')

# Saving the \docs path
destino <- getwd()

# Returning to original path
setwd(original_wd)

# Defining _book as work directory
setwd('_book')

# List of files to be copied
html_files_folders <- list.files()

# Copying the files from _books to \docs folder
file.copy(html_files_folders, to = destino,overwrite = TRUE)

# Defining the original Work Directory
setwd(original_wd)
```