--- 
title: "ND111 - Notebook"
subtitle: "Hi everybody"
author: "AH Uyekita"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---

# Prerequisites

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```


```{r,message=FALSE,include=FALSE}
# Saving the original Work Directory
original_wd <- getwd()

# Goes to the parents level - Where the files will be rendered
setwd('..')

# Saving the \docs path
destino <- getwd()

# Returning to original path
setwd(original_wd)

# Defining _book as work directory
setwd('_book')

# List of files to be copied
html_files_folders <- list.files()

# Copying the files from _books to \docs folder
file.copy(html_files_folders, to = destino,overwrite = TRUE)

# Defining the original Work Directory
setwd(original_wd)
```